Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-10 edubots_surveys.Rnw
Review RQ4 and few small edits all over

In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.} or the introduction of new degrees) crisis could be an opportunity to introduce new technologies. The reason being that it does not
bring major changes in attitude 
%(as a minor "crisis" we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}), 
%or simply the introduction of new degrees. 
Although changes driven by external forces do offer the chance of piloting new technologies, they do not
seem to bring internal changes in educators' attitudes (which, after all, is
bound to be the same). In absence of a clear answer in this direction, the right
moment to introduce new technologies is always when the IT and managing staff is
ready to support it (since, as we have seen before, "official" support is one of
the factors that is most valued by teachers).

>>>>

In our survey, we could not find an answer about the right moment to introducing chatbot technologies. The response to questions regarding to change of
behavior during and after the first stay-at-home stage of the pandemic do not suggest that a major (or minor, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.} or the introduction of new degrees) crisis could be an opportunity to introduce new technologies. The reason being that it does not
bring major changes in attitude 
%(as a minor ``crisis'' we could mention any institutional event that brings about methodological changes, such as new higher education laws\footnote{We seem to have one of these, at least in Spain, every 10 years or so.}), 
%or simply the introduction of new degrees. 
Although changes driven by external forces do offer the chance of piloting new technologies, they do not
seem to bring internal changes in educators' attitudes (which, after all, is
bound to be the same). In absence of a clear answer in this direction, the right
moment to introduce new technologies is always when the IT and managing staff is
ready to support it (since, as we have seen before, ``official'' support is one of
the factors that is most valued by teachers).
